\documentclass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=10.0in %How tall the text body is allowed to be on each page


\setlength{\voffset}{-0.45in}
\setlength{\headsep}{4pt}


\newcommand{\name}[1]{
  \centerline{\Huge{#1}}
  }
\date{} 

  



\begin{document}
\thispagestyle{empty}
\name{Nathan St. Amour}
\begin{center}
%\centerline{\large{\begin{bf}Permanent:\end{bf} 7589 Glen Meadow Dr }}

%\centerline{\large{ West Chester, Ohio 45069}}
 
% \centerline{\large{\begin{bf}School:\end{bf} 22 University Terr, Bryan Hall}}
 
% \centerline{\large{Athens, Ohio 45701}} 
\centerline{\large{Email: ns196414@ohio.edu}}
\centerline{GitHub: https://github.com/neewamp}
\centerline{\large{Phone: (513)-593-4855}}

\end{center}
\subsection*{Objective}
 Summer internship possibly leading to full time positions in Computer Science. My interests are in designing correct, efficient software and bioinformatics preferably in a team environment.
 \subsection*{Education}
 Bachelor of Science in Computer Science; Expected graduation: May 2018\\
 Major GPA   3.466/4.00 \\
 Cumulative GPA   3.347/4.000


 \subsection*{Notable Coursework}
Software Verification, IOT \& Wireless Networking, Data Mining,
Algorithms
%% Data Structures CS 3610, , , Intro to Computer Science CS 2401(C\texttt{++}), Introduction to Logical Design EE 1024, Calculus 2, Discrete Math CS 3000, Software Engineering Tools and Practice CS 3560, Professional and Ethical Computing CS 2650.
\subsection*{Languages}


%\begin{bf}\emph {Operating systems}:\end{bf}\textbf { Microsoft Windows}: Microsoft Office Suite and Visual Studio, \textbf{Linux}:  Latex, Bash,  etc.\\

%% \begin{bf}\emph {Languages}:\end{bf}
C\texttt{++}, Python, Coq, Ocaml; understanding of: Haskell, C$^\texttt{\#}$, Perl, SQL, HTML, Java Script and CSS 
\subsection*{Tools}
Proficient with Linux, Latex, Emacs and Git; understanding of Visual Studio.

%\begin{bf}\emph {Structure}:\end{bf} MVC

\subsection*{Affiliations}
\texttt{ACM} Ohio University chapter of the Association for Computing Machinery
\begin{itemize}
\item Perform essential tasks as treasurer. This includes: writing proposals to acquire funding for events, handling budget and reimbursements for day to day expenses and organizing fund raising projects.
\item Placed well in a competative setting after solving a problem with a team at ICPC 2015. ICPC is a collegiate programming contest where a team works to solve challenging programming problems. 
\end{itemize}
\subsection*{Professional Experience} 
\texttt{Undergraduate Research}, with Dr. Gordan Stewart \\
Verification: \\
Working to develop a verified implementation of graphs and graph algorithms in the theorem prover Coq.  Beginning to collaborate with other students after teaching the theorem prover.\\ \\
\texttt{Research Assistant}, Vis lab Ohio University \\
%% June 2016 \textbf{--} ongoing\\
Bioinformatics: \\
Used open source software and custom programs to sequence the genome of a red algae,\textit{ Balbiania investiens}. This was after working with a team to determine how to sequence the genome. Currently involved in writing a paper to be submited for review in a few months.
           
\end{document}
